Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}

### 2020-03-19 paper.tex
Add Related Work Section

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

>>>>

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\section{Related Work}

Several papers proposed various types of approaches to improve the overall efficiency of the multilevel feedback queue scheduling algorithm. The chosen quantum time for each queue plays a major role. For instance, in paper [] The highest priority queue has been given a relatively low quantum period, and as the priority of a queue decreases, its quantum gets multiplied by a constant which greatly prevents starvation for lower priority processes. Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance. In paper [6], a new algorithm is presented for solving these drawbacks and minimizing the response time. In this algorithm, a Recurrent Neural Network was used to determine both the number of queues and the optimized time quantum value for each queue. The RNN generates the most effective model to compute the time quantum value. Their proposed intelligent version of the MLFQ promises good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm. Our approach uses an optimized version of RR named shortest remaining burst round-robin (SRBRR) as in paper [4] avoids the learning time in paper [6]. Regarding MLFQ, various approaches have been made and researches have been carried to improve its efficiency. Those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority. However, our approach deals with starvation not by only having dynamic quantum value but by boosting processes from lower priority queues to higher ones according to a specific policy.
